Reproduction frequency and offspring survival decline in elephant seals past prime age

### 2024-10-15 paper/paperv3.qmd
Updating the detection probability figure

sighting_img <- sealdat %>% 
  group_by(animalID) %>% 
  summarize(yearborn = yearborn[1],
            first_obs = min(year),
            last_obs = max(year),
            .groups = "keep") %>% 
  reframe(yearborn = yearborn,
          year = yearborn:last_obs,
          age = year - yearborn,
          prerecruit = year < first_obs) %>% 
  left_join(sealdat %>% 
              group_by(animalID, year) %>% 
              summarize(observed_int = max(observed_int),
                        .groups = "drop"),
            by = c("animalID", "year")) %>% 
  mutate(
    observed = case_when(
      age == 0 ~ "Born",
      prerecruit ~ "Pre-recruit",
      observed_int == 0 ~ "Non-breeder",
      observed_int == 1 ~ "Breeder",
      is.na(observed_int) ~ "Unobserved"
    ),
    observed = factor(observed, levels = c("Born",
                                           "Pre-recruit",
                                           "Non-breeder",
                                           "Breeder",
                                           "Unobserved"))
  ) %>% 
  group_by(animalID) %>% 
  mutate(lastrepro = max(age),
         yearborn = na.omit(yearborn)[1]) %>% 
  ungroup() %>% 
  arrange(yearborn, lastrepro, animalID) %>% 
  mutate(animalID = factor(animalID, levels = unique(animalID))) %>% 
  filter(year > 1987) %>% 
  ggplot(aes(year, animalID)) +
  geom_raster(aes(fill = observed)) +
  scale_fill_brewer(palette = "YlGnBu", direction = 1) +
  guides(fill = guide_legend(position = "inside", 
                             direction = "horizontal",
                             ncol = 1,
                             byrow = TRUE)) +
  labs(y ="Individual") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.x = element_blank(),
        legend.title = element_blank(),
        legend.position = c(0.1, 0.95),
        legend.justification = c(0, 1),
        legend.background = element_blank(),
        legend.key.size = unit(4, "mm"),
        legend.text = element_text(size = 8))

@@

ggplot(detection_pred, aes(age, color = age_cat, fill = age_cat)) +
  # Line per year
  geom_line(aes(y = predicted, group = interaction(age_cat, year_fct)), 
            detection_pred_years, 
            alpha = 0.2) +
  # Weighted model
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high),
              alpha = 0.3, 
              color = NA) +
  geom_line(aes(y = predicted, linetype = age_cat),
            linewidth = 1.5) +
  # Population-level model
  geom_line(aes(y = pred_pop), 
            linetype = "dotted",
            linewidth = 1.1) +
  # Raw data
  geom_pointrange(aes(y = observed_mean, 
                      ymin = observed_lwr, 
                      ymax = observed_upr),
                  detection_summ) +
  # Sample size
  geom_text(aes(age, label = n), detection_summ, y = 0, vjust = 0) +
  scale_x_continuous("Age", breaks = seq(4, 19, by = 4)) +
  scale_y_continuous("Detection rate", 
                     labels = scales::label_percent(accuracy = 1),
                     limits = c(0, NA)) +
  scale_linetype_manual(values = c("solid", "dashed")) +
  scale_color_manual(values = c("#7fbc41", "#de77ae")) +
  scale_fill_manual(values = c("#7fbc41", "#de77ae")) +
  theme(legend.position = "none")
```

>>>>

sighting_img <- sealdat %>% 
  group_by(animalID) %>% 
  summarize(yearborn = yearborn[1],
            first_obs = min(year),
            last_obs = max(year),
            .groups = "keep") %>% 
  reframe(yearborn = yearborn,
          year = yearborn:last_obs,
          age = year - yearborn,
          prerecruit = year < first_obs) %>% 
  left_join(sealdat %>% 
              group_by(animalID, year) %>% 
              summarize(observed_int = max(observed_int),
                        .groups = "drop"),
            by = c("animalID", "year")) %>% 
  mutate(
    observed = case_when(
      age == 0 ~ "Born",
      prerecruit ~ "Pre-recruit",
      observed_int == 0 ~ "Non-breeder",
      observed_int == 1 ~ "Breeder",
      is.na(observed_int) ~ "Unobserved"
    ),
    observed = factor(observed, levels = c("Born",
                                           "Pre-recruit",
                                           "Non-breeder",
                                           "Breeder",
                                           "Unobserved"))
  ) %>% 
  group_by(animalID) %>% 
  mutate(lastrepro = max(age),
         yearborn = na.omit(yearborn)[1]) %>% 
  ungroup() %>% 
  arrange(yearborn, lastrepro, animalID) %>% 
  mutate(animalID = factor(animalID, levels = unique(animalID))) %>% 
  filter(year > 1987) %>% 
  ggplot(aes(year, animalID)) +
  geom_raster(aes(fill = observed)) +
  scale_fill_viridis_d(direction = 1) +
  guides(fill = guide_legend(position = "inside", 
                             direction = "horizontal",
                             ncol = 1,
                             byrow = TRUE)) +
  labs(y ="Individual") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.x = element_blank(),
        legend.title = element_blank(),
        legend.position = c(0.1, 0.95),
        legend.justification = c(0, 1),
        legend.background = element_blank(),
        legend.key.size = unit(4, "mm"),
        legend.text = element_text(size = 8))

@@

ggplot(detection_pred, aes(age)) +
  # Line per year
  geom_line(aes(y = predicted, group = interaction(age, year_fct)), 
            detection_pred_years, 
            alpha = 0.2) +
  # Weighted model
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high),
              alpha = 0.3, 
              color = NA) +
  geom_line(aes(y = predicted),
            linewidth = 1.5) +
  # Population-level model
  geom_line(aes(y = pred_pop), 
            linetype = "dotted",
            linewidth = 1.1) +
  # Raw data
  geom_pointrange(aes(y = observed_mean, 
                      ymin = observed_lwr, 
                      ymax = observed_upr),
                  detection_summ) +
  # Sample size
  geom_text(aes(age, label = n), detection_summ, y = 0, vjust = 0) +
  scale_x_continuous("Age", breaks = seq(4, 19, by = 4)) +
  scale_y_continuous("Detection rate", 
                     labels = scales::label_percent(accuracy = 1),
                     limits = c(0, NA)) +
  # scale_linetype_manual(values = c("solid", "dashed")) +
  # scale_color_manual(values = c("#7fbc41", "#de77ae")) +
  # scale_fill_manual(values = c("#7fbc41", "#de77ae")) +
  theme(legend.position = "none")
```
